A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-08 paper_v02/article.tex
tests page link
article first version finished

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Fernando Ferraz Ribeiro~\orcidlink{0000-0002-0685-4774}\\Federal University of Bahia
   \And Gilney Figueira Zebende~\orcidlink{0000-0003-2420-9805}\\Universidade Estadual\\de Feira de Santana}
\Plainauthor{Fernando Ferraz Ribeiro, Gilney Figueira Zebende}
%  and $DMC_x^2$
%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$}
\Plaintitle{A Python/Zig optimized and customizable implementation for the Pdcca and DMCx2 methods}
\Shorttitle{\proglang{Python}/\proglang{Zig} implementation for the $\rho_{DCCA}$ and $DMC_x^2$}

%% - \Abstract{} almost as usual
\Abstract{
  This paper presents tha \pkg{Zebende}, a \proglang{Python} package written in \proglang{Python} and \proglang{Zig}, that calculates the $DFA$, $DCCA$ $\rho_{DCCA}$ and the $DMC_x^2$. The package presents an optimized algorithm that significantly improves the calculations speed. A comparison with other packages that calculates the $\rho_{DCCA}$. The package is also the first to implement the $DMC_x^2$ coefficient in a package and the first algorithm to calculates it for any number of time series.
}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Fernando Ferraz Ribeiro\\
  Universidade Federal da Bahia\\
  Faculty of Achitecture\\
  Universit\"at Innsbruck\\
  Universit\"atsstr.~15\\
  6020 Innsbruck, Austria\\
  E-mail: \email{fernando.ribeiro@ufba.br}\\
  \emph{and}\\
  Centro Universitário Senai-Cimatec\\

  % URL: \url{https://www.zeileis.org/}
}

>>>>

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Fernando Ferraz Ribeiro~\orcidlink{0000-0002-0685-4774}\\Federal University of Bahia
   \And Gilney Figueira Zebende~\orcidlink{0000-0003-2420-9805}\\State University\\of Feira de Santana}
\Plainauthor{Fernando Ferraz Ribeiro, Gilney Figueira Zebende}
%  and $DMC_x^2$
%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$}
\Plaintitle{A Python/Zig optimized and customizable implementation for the Pdcca and DMCx2 methods}
\Shorttitle{\proglang{Python}/\proglang{Zig} implementation for the $\rho_{DCCA}$ and $DMC_x^2$}

%% - \Abstract{} almost as usual
\Abstract{
  This paper presents \pkg{Zebende}, a \proglang{Python} package written in \proglang{Python} and \proglang{Zig}, that calculates the $DFA$, $DCCA$ $\rho_{DCCA}$ and the $DMC_x^2$, along with auxiliary functions to help the calculations process. The package presents an optimized algorithm that significantly improves the calculations speed in large datasets. \pkg{Zebende} is the first package that implements the $DMC_x^2$ and can be applied to any number of time series. The optimized version of the algorithm is compared to the standard implementation, presenting valuable performance increase. A comparison with other \proglang{Python} and \proglang{R} packages that calculates the $\rho_{DCCA}$ is also presented.}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Fernando Ferraz Ribeiro\\
  Faculty of Achitecture\\
  Federal University of Bahia\\
  Caetano Moura street, 121, \\
  40210-905, Salvador-BA, Brazil\\
  E-mail: \email{fernando.ribeiro@ufba.br}\\
  URL: \url{https://arquitetura.ufba.br/}\\
  \emph{and}\\
  Graduate Program in Modeling in Earth and Environmental Sciences\\
  State University of Feira de Santana\\
  Av. Transnordestina\\
  44036-900, Feira de Santana-BA, Brazil\\
  URL: \url{https://ppgm.uefs.br/}\\
  \emph{and}\\
  Senai-Cimatec University\\
  Av. Orlando Gomes, 1845,\\
  41650-010, Salvador-BA, Brazil \\
  URL: \url{https://www.senaicimatec.com.br/}\\
  \\
  Gilney Figueira Zebende\\
  Graduate Program in Modeling in Earth and Environmental Sciences\\
  State University of Feira de Santana\\
  Av. Transnordestina\\
  44036-900, Feira de Santana-BA, Brazil\\
  E-mail: \email{gfzebende@uefs.br}\\
  URL: \url{https://ppgm.uefs.br/}\\
}
